This is a methods report of a rejected instrument: a preregistered, zero-human, multi-family LLM content-analysis design whose fresh-data reliability checkpoint failed on all four coding dimensions at the start of the confirmatory run, halting the study under its frozen decision tree before any hypothesis was tested. The case was to be a corpus-scale audit of natural theology's inferential chain: The inferential chain from a bare first cause to the God of Nicene Christianity has been discussed piecewise --- as the ``gap problem,'' as ``ramified natural theology,'' as the ``dwindling probabilities'' debate --- but never measured as a whole. We introduce a witness-based criterion for individuating the chain's logically independent steps, yielding an eight-step canonical partition whose burden count is invariant under definitional bundling. We then designed, and preregistered in full, an audit of twenty-one issue-years (2004--2024) of the peer-reviewed philosophy-of-religion literature --- 3,536 articles across eleven journals in three venue tiers, locked with the post-2008 stratum as the primary confirmatory population --- under which each article's step, direction, claim strength, and the epistemic type of its load-bearing evidence was to be coded. All coding was to be performed by a fixed, preregistered, multi-family LLM instrument with zero human item-coding, gated by a preregistered contamination-control battery. Two hypotheses were preregistered: (1) that among positive evidential claims, pro-side items are predominantly a priori and contra-side items predominantly empirical or historical (registered odds ratio $\ge$ 3); (2) that positive evidential pro-side claims are more prevalent in confessionally affiliated than in mainstream venues. The subfield's majority-theist composition biases against the second prediction --- a point about the test's stringency, not its outcome. A preregistered kill criterion binds the symmetric case: a two-null result downgrades the project to a descriptive-map preprint, with no journal claim. Neither hypothesis was tested. At the start of the confirmatory run, the preregistered reliability checkpoint --- 150 fresh, seed-drawn items, each coded by three model families with three independent runs per family under the frozen instrument --- failed its preregistered dual statistic on all four coding dimensions: the point criterion on two (minimum pairwise Krippendorff's $\alpha$ .676--.736 against the .70 floor) and the bootstrap lower-bound criterion on all four (95\% lower bounds .390--.650 against the .667 floor), with the run-level determinism audits (B1a/B1b) clean and the preregistered family-correlation watch untriggered. Under the frozen decision tree this halts all coding, blocks every confirmatory claim, and resolves the pilot gate's conditional declaration negatively: the pilot reliability that licensed the instrument --- explicitly flagged in the preregistration as a selected estimate under optional stopping --- did not survive contact with fresh data. The paper accordingly reports the measurement design, the validation battery, the locked corpus infrastructure, and the complete preregistered trajectory ending in instrument rejection, as a methods contribution and a cautionary result for LLM-based content analysis: a preregistered fresh-data reliability checkpoint is cheap relative to a full run, and it does exactly what it is designed to do.
