\emph{Keywords:} large language models; automated content analysis; inter-rater reliability; Krippendorff's alpha; protocol precommitment; confirmatory checkpoint; zero-human annotation; validation battery; philosophy of religion; natural theology; Lessing's ditch.

\textbf{How to read this document (added at v0.3, 2026-07-17).} The paper's sole confirmatory result is \S{}5.1.1 --- the confirmatory checkpoint that rejected the instrument --- and its methods contribution lives in \S{}4 (the zero-human instrument and its validation battery; \S{}4.4.10 tabulates the battery at a glance). Sections 2--3 build the case-study apparatus: a witness-based criterion that motivates an eight-step working partition of natural theology's inferential chain (\S{}7.2 states what is and is not claimed for it), with \S{}7 proving a burden-invariance result that stands independently of the halted audit; \S{}8 answers objections to the design. Sections 5.2--5.7 and 6 are precommitted result shells resolved to \emph{not run}: they are preserved in place, unfilled with outcome data (their resolution markers are dated and inventoried), because the outcome-blind commit history of these shells is part of the paper's evidentiary claim --- in the spirit of the Registered Reports program's commitment to outcome-independent publication (Chambers and Tzavella 2022) --- though this is a self-sealed study with a locally frozen decision tree, not a journal-reviewed Registered Report. Methods readers: \S{}4, \S{}5.1.1, \S{}4.4.10. Philosophy readers: \S{}\S{}2--3, \S{}7, \S{}8. The change inventories of record are the back-matter resolution notes (v0.2 for the P4 resolution; v0.3 for this repositioning; v0.4--v0.12 for the post-review repairs and the v0.9 correction of record), preceded by a version-history summary. \emph{Terminology (v0.10; extended v0.11).} Following the v0.9 correction, the paper's own voice says \emph{precommitted}, \emph{prospectively frozen}, or \emph{sealed} where earlier versions said ``preregistered'' (and, for the project's own acts, ``registered''): the protocol was frozen locally under a SHA256 manifest, without the externally timestamped registration the earlier label implied. The frozen result shells (\S{}\S{}5.2--5.7, \S{}6), verbatim quotations from the sealed documents, artifact names retaining the historical prefix (\texttt{PREREG\_MANIFEST.txt}; the \texttt{prereg-guardian} agent), the proper noun Registered Reports, and the dated revision notes below keep the original vocabulary; references to the OSF event itself, ledger nouns (the decision and threshold registers), and the linguistic sense of ``register'' are not freeze-vocabulary and stand as written.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
