\section*{References}
% 61 entries web-verified against publisher/DOI records (2026-07-17);
% the four flagged judgment calls approved by the author 2026-07-20.
% v0.4 (2026-07-20): 14 entries added (10 methods/infrastructure + 4
% witness-note sources); all 14 web-verified 2026-07-20, no corrections.
% v0.7 (2026-07-20): 4 entries added (Adang 1996; Lapide & Moltmann 1981;
% Ostler 2001; Tindal 1730); all web-verified 2026-07-20.
% Verification scope, all passes: bibliographic existence and metadata
% against publisher/authoritative records; interpretive uses are documented
% separately (verification memos in analysis/audit-exports/).
\begingroup
\setlength{\parindent}{0pt}\setlength{\parskip}{5pt}
\newcommand{\entry}[1]{\par\hangindent=1.5em\hangafter=1 #1}

\entry{Abdel Haleem, M.~A.~S. (trans.) (2004). \emph{The Qur'an: A New Translation}. Oxford University Press (Oxford World's Classics; reissued with corrections, 2008).}
\entry{Adams, F.~C. (2019). The degree of fine-tuning in our universe --- and others. \emph{Physics Reports}, 807, 1--111.}
\entry{Adang, C. (1996). \emph{Muslim Writers on Judaism and the Hebrew Bible: From Ibn Rabban to Ibn Hazm}. Brill.}
\entry{Allison, D.~C., Jr. (2021). \emph{The Resurrection of Jesus: Apologetics, Polemics, History}. T\&T Clark.}
\entry{Alston, W.~P. (1991). \emph{Perceiving God: The Epistemology of Religious Experience}. Cornell University Press.}
\entry{Barnes, L.~A. (2012). The fine-tuning of the universe for intelligent life. \emph{Publications of the Astronomical Society of Australia}, 29(4), 529--564.}
\entry{Benson, H., Dusek, J.~A., Sherwood, J.~B., et al. (2006). Study of the Therapeutic Effects of Intercessory Prayer (STEP) in cardiac bypass patients: A multicenter randomized trial of uncertainty and certainty of receiving intercessory prayer. \emph{American Heart Journal}, 151(4), 934--942.}
\entry{Berger, D. (1979). \emph{The Jewish-Christian Debate in the High Middle Ages: A Critical Edition of the Ni\d{z}\d{z}a\d{h}on Vetus}. Jewish Publication Society.}
\entry{Borde, A., Guth, A.~H., and Vilenkin, A. (2003). Inflationary spacetimes are incomplete in past directions. \emph{Physical Review Letters}, 90(15), 151301.}
\entry{Bostrom, N. (2003). Are you living in a computer simulation? \emph{Philosophical Quarterly}, 53(211), 243--255.}
\entry{Bourget, D., and Chalmers, D.~J. (2014). What do philosophers believe? \emph{Philosophical Studies}, 170(3), 465--500.}
\entry{Bourget, D., and Chalmers, D.~J. (2023). Philosophers on philosophy: The 2020 PhilPapers survey. \emph{Philosophers' Imprint}, 23(11).}
\entry{Brower, J.~E., and Rea, M.~C. (2005). Material constitution and the Trinity. \emph{Faith and Philosophy}, 22(1), 57--76.}
\entry{Bystranowski, P., Dranseika, V., and \.{Z}uradzki, T. (2022). Half a century of bioethics and philosophy of medicine: A topic-modeling study. \emph{Bioethics}, 36(9), 902--925.}
\entry{Cahn, S.~M. (1977). Cacodaemony. \emph{Analysis}, 37(1), 69--73.}
\entry{Carnley, P. (1987). \emph{The Structure of Resurrection Belief}. Clarendon Press.}
\entry{Carnley, P. (2019). \emph{Resurrection in Retrospect: A Critical Examination of the Theology of N.~T. Wright}. Cascade Books.}
\entry{Chambers, C.~D., and Tzavella, L. (2022). The past, present and future of Registered Reports. \emph{Nature Human Behaviour}, 6(1), 29--42.}
\entry{De Cruz, H. (2017). Religious disagreement: An empirical study among academic philosophers. \emph{Episteme}, 14(1), 71--87.}
\entry{De Cruz, H. (2018). Religious beliefs and philosophical views: A qualitative study. \emph{Res Philosophica}, 95(3), 477--504.}
\entry{De Cruz, H., and De Smedt, J. (2016). How do philosophers evaluate natural theological arguments? An experimental philosophical investigation. In H.~De Cruz and R.~Nichols (eds.), \emph{Advances in Religion, Cognitive Science, and Experimental Philosophy} (pp. 119--142). Bloomsbury Academic.}
\entry{Draper, P. (1989). Pain and pleasure: An evidential problem for theists. \emph{No\^{u}s}, 23(3), 331--350.}
\entry{Draper, P., and Nichols, R. (2013). Diagnosing bias in the philosophy of religion. \emph{The Monist}, 96(3), 420--446.}
\entry{Duan, M., Suri, A., Mireshghallah, N., Min, S., Shi, W., Zettlemoyer, L., Tsvetkov, Y., Choi, Y., Evans, D., and Hajishirzi, H. (2024). Do membership inference attacks work on large language models? \emph{First Conference on Language Modeling (COLM)}. arXiv:2402.07841.}
\entry{Efron, B., and Tibshirani, R.~J. (1993). \emph{An Introduction to the Bootstrap}. Chapman \& Hall.}
\entry{Fisher, R.~A. (1934). \emph{Statistical Methods for Research Workers} (5th ed.). Oliver and Boyd.}
\entry{Friedmann, Y. (1986). Finality of prophethood in Sunni Isl\={a}m. \emph{Jerusalem Studies in Arabic and Islam}, 7, 177--215.}
\entry{Gauch, H.~G., Jr. (2013). The methodology of ramified natural theology. \emph{Philosophia Christi}, 15(2), 283--298.}
\entry{Geach, P.~T. (1973). Omnipotence. \emph{Philosophy}, 48(183), 7--20.}
\entry{Haldane, J.~B.~S. (1956). The estimation and significance of the logarithm of a ratio of frequencies. \emph{Annals of Human Genetics}, 20(4), 309--311.}
\entry{Hanley, J.~A., and McNeil, B.~J. (1982). The meaning and use of the area under a receiver operating characteristic (ROC) curve. \emph{Radiology}, 143(1), 29--36.}
\entry{Hartshorne, C. (1984). \emph{Omnipotence and Other Theological Mistakes}. State University of New York Press.}
\entry{Hasker, W. (1989). \emph{God, Time, and Knowledge}. Cornell University Press.}
\entry{Hick, J. (1989). \emph{An Interpretation of Religion: Human Responses to the Transcendent}. Yale University Press / Macmillan.}
\entry{Holder, R. (2021). \emph{Ramified Natural Theology in Science and Religion: Moving Forward from Natural Theology}. Routledge.}
\entry{Hume, D. (1748). Of miracles. Section X of \emph{An Enquiry Concerning Human Understanding}.}
\entry{Kinney, R., Anastasiades, C., Authur, R., et al. (2023). The Semantic Scholar Open Data Platform. arXiv:2301.10140.}
\entry{Krippendorff, K. (2004). \emph{Content Analysis: An Introduction to Its Methodology} (2nd ed.). Sage.}
\entry{Lapide, P. (1983). \emph{The Resurrection of Jesus: A Jewish Perspective} (W.~C. Linss, trans.). Augsburg.}
\entry{Lapide, P., and Moltmann, J. (1981). \emph{Jewish Monotheism and Christian Trinitarian Doctrine: A Dialogue} (L.~Swidler, trans.). Fortress Press.}
\entry{Law, S. (2010). The evil-god challenge. \emph{Religious Studies}, 46(3), 353--373.}
\entry{Leslie, J. (1979). \emph{Value and Existence}. Basil Blackwell.}
\entry{Lessing, G.~E. (1777). \"{U}ber den Beweis des Geistes und der Kraft. English translation: On the proof of the spirit and of power. In H.~Chadwick (ed.), \emph{Lessing's Theological Writings} (pp. 51--56). Stanford University Press, 1957.}
\entry{L\"{u}demann, G. (1994). \emph{The Resurrection of Jesus: History, Experience, Theology}. Fortress Press.}
\entry{Maimonides, M. (1987). \emph{Mishneh Torah: Hilchot Melachim U'Milchamoteihem --- The Laws of Kings and Their Wars} (E.~Touger, trans.). Moznaim. (Uncensored text of 11:4, restored from Yemenite manuscripts and early uncensored printings.)}
\entry{Malpass, A., and Morriston, W. (2020). Endless and infinite. \emph{The Philosophical Quarterly}, 70(281), 830--849.}
\entry{Mann, H.~B., and Whitney, D.~R. (1947). On a test of whether one of two random variables is stochastically larger than the other. \emph{Annals of Mathematical Statistics}, 18(1), 50--60.}
\entry{McGrew, T. (2004). Has Plantinga refuted the historical argument? \emph{Philosophia Christi}, 6(1), 7--26.}
\entry{McGrew, T., and McGrew, L. (2006). On the historical argument: A rejoinder to Plantinga. \emph{Philosophia Christi}, 8(1), 23--38.}
\entry{McGrew, T., McGrew, L., and Vestrup, E. (2001). Probabilities and the fine-tuning argument: A sceptical view. \emph{Mind}, 110(440), 1027--1038.}
\entry{Mill, J.~S. (1874). Theism. In \emph{Three Essays on Religion}. Longmans, Green.}
\entry{Morris, T.~V. (1986). \emph{The Logic of God Incarnate}. Cornell University Press.}
\entry{Morriston, W. (2000). Must the beginning of the universe have a personal cause? \emph{Faith and Philosophy}, 17(2), 149--169.}
\entry{Nickel, G. (2015). Dwindling probability: Mathematical and philosophical notes in margin. In D.~Sch\"{o}necker (ed.), \emph{Plantinga's Warranted Christian Belief: Critical Essays with a Reply by Alvin Plantinga} (pp. 213--236). De Gruyter.}
\entry{Ocampo, S.~T. (2024). Strategies for Stage II of cosmological arguments. \emph{International Journal for Philosophy of Religion}, 96(1), 55--88.}
\entry{Oppy, G. (2006). \emph{Arguing about Gods}. Cambridge University Press.}
\entry{Ostler, B.~T. (2001). \emph{Exploring Mormon Thought: Vol. 1, The Attributes of God}. Greg Kofford Books.}
\entry{Plantinga, A. (1974). \emph{The Nature of Necessity}. Oxford University Press.}
\entry{Plantinga, A. (2000). \emph{Warranted Christian Belief}. Oxford University Press.}
\entry{Plantinga, A. (2006). Historical arguments and dwindling probabilities: A response to Timothy McGrew. \emph{Philosophia Christi}, 8(1), 7--22.}
\entry{Priem, J., Piwowar, H., and Orr, R. (2022). OpenAlex: A fully-open index of scholarly works, authors, venues, institutions, and concepts. arXiv:2205.01833.}
\entry{Pruss, A.~R. (2009). The Leibnizian cosmological argument. In W.~L. Craig and J.~P. Moreland (eds.), \emph{The Blackwell Companion to Natural Theology} (pp. 24--100). Wiley-Blackwell.}
\entry{Pruss, A.~R., and Rasmussen, J.~L. (2018). \emph{Necessary Existence}. Oxford University Press.}
\entry{Rasmussen, J. (2009). From a necessary being to God. \emph{International Journal for Philosophy of Religion}, 66(1), 1--13.}
\entry{Rembaum, J.~E. (1982). The development of a Jewish exegetical tradition regarding Isaiah 53. \emph{Harvard Theological Review}, 75(3), 289--311.}
\entry{Roberts, L., Ahmed, I., Hall, S., and Davison, A. (2009). Intercessory prayer for the alleviation of ill health. \emph{Cochrane Database of Systematic Reviews}, 2009(2), CD000368.}
\entry{Roche, W., and Shogenji, T. (2014). Dwindling confirmation. \emph{Philosophy of Science}, 81(1), 114--137.}
\entry{Rowe, W.~L. (1979). The problem of evil and some varieties of atheism. \emph{American Philosophical Quarterly}, 16(4), 335--341.}
\entry{Russell, B., and Copleston, F.~C. (1948/1957). The existence of God: A debate. In B.~Russell, \emph{Why I Am Not a Christian and Other Essays} (P.~Edwards, ed.). George Allen \& Unwin.}
\entry{Steinhart, E. (2010). Theological implications of the simulation argument. \emph{Ars Disputandi}, 10(1), 23--37.}
\entry{Swinburne, R. (2003). \emph{The Resurrection of God Incarnate}. Oxford University Press.}
\entry{Swinburne, R. (2004a). \emph{The Existence of God} (2nd ed.). Clarendon Press.}
\entry{Swinburne, R. (2004b). Natural theology, its ``dwindling probabilities'' and ``lack of rapport''. \emph{Faith and Philosophy}, 21(4), 533--546.}
\entry{Tegmark, M. (2008). The mathematical universe. \emph{Foundations of Physics}, 38(2), 101--150.}
\entry{Tindal, M. (1730). \emph{Christianity as Old as the Creation: or, The Gospel, a Republication of the Religion of Nature}. London.}
\entry{Tuggy, D. (2003). The unfinished business of Trinitarian theorizing. \emph{Religious Studies}, 39(2), 165--183.}
\entry{Wang, X., Wei, J., Schuurmans, D., Le, Q., Chi, E., Narang, S., Chowdhery, A., and Zhou, D. (2023). Self-consistency improves chain of thought reasoning in language models. \emph{Eleventh International Conference on Learning Representations (ICLR)}. arXiv:2203.11171.}
\entry{White, R. (2000). Fine-tuning and multiple universes. \emph{No\^{u}s}, 34(2), 260--276.}
\entry{Wildman, W.~J. (2004). The Divine Action Project, 1988--2003. \emph{Theology and Science}, 2(1), 31--75.}
\entry{Wiles, M. (1986). \emph{God's Action in the World: The Bampton Lectures for 1986}. SCM Press.}
\entry{Woolf, B. (1955). On estimating the relation between blood group and disease. \emph{Annals of Human Genetics}, 19, 251--253.}
\entry{Wright, N.~T. (2003). \emph{The Resurrection of the Son of God}. Fortress Press.}
\entry{Wykstra, S.~J. (1984). The Humean obstacle to evidential arguments from suffering: On avoiding the evils of ``appearance''. \emph{International Journal for Philosophy of Religion}, 16(2), 73--93.}
\endgroup
